Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-07-01 paper/main.tex
some changes to manuscript & references.bib
revision of intro

\todo[inline]{our system cannot accept BibTeX bibliography files; authors who
    wish to use BibTeX to prepare their references should therefore copy the
    refernce list from the .bbl file that BibTeX generates and paste it into the
    main manuscript .tex file (and delete the associated
    \textbackslash{}bibliography and \textbackslash{}bibliographystyle
commands)}

\todo[inline]{Ich arbeite erstmal wie gehabt mit der references.bib
    und habe oben usepackage{natbib}' eingefügt}

\section{Introduction} Cognitive neuroscientists use brain imaging methods like
blood oxygenation level-dependent functional magnetic resonance imaging (BOLD
fMRI) to map perceptual and cognitive brain processes (e.g. viewing of
landscapes, \citep{epstein1998ppa}; or theory of mind
\citep{spunt2014validating}) to functional brain areas or networks. Brain
mapping studies have traditionally employed small sets of carefully chosen,
simplified stimuli to strictly control experimental conditions and facilitate
functional isolation of brain areas. The disadvantage is that a limited number
of simplified stimuli does not resemble our real-life experience and lacks
external validity \citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}. Additionally, brain mapping studies usually
average results across at least 10-15 subjects to improve the
signal-to-noise-ratio (SNR). The disadvantage here is that the averaging
approach does not characterize brain functions at an individual level, a
prerequisite for the application of brain imaging methods in individual
diagnostics (cf. \citep{dubois2016building})

@@

% Was ist PPA?
A classic example of a functional, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}. The PPA is located in the posterior parahippocampal
gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus,
both being part of the ventral visual stream \citep{mishkin1982contribution,
goodale1992separate}. Increased hemodynamic activity in the PPA correlates with
the perception of static pictures of landscapes or landmarks compared to
pictures of tools or faces.  According to the spatial layout hypothesis, the PPA
is involved in processing the surface geometry of a visual stimulus and possibly
in identifying scenes based on their spatial layout \citep{epstein2010reliable}.

% Literature Review PPA: Einleitung
At a group avergae level, results generalize to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}. One study that used spoken, place-related
sentences showed significantly decreased activation in the left and no
modulation in the right-hemispheric PPA \citep{aziz2008modulation}.

% Studien im Einzelnen: O'Craven: Mental imagery
In the study conducted by \citep{ocraven2000mental} participants viewed
alternating blocks of pictures showing famous faces and familiar places during
an initial experimental paradigm. In a subsequent paradigm, participants were
instructed to ``form a vivid mental image'' of the previously viewed pictures.
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.

@@

\todo[inline]{Ihre Method Section ist strange und es bei ihr überall eh nur
    uneinheitliche Grütze heraus; Ich blicke nicht durch; was folgend kommt,
    wird nicht vollständig korrekt sein. So wie ich es verstanden habe, hat sie
    den Unterschied zwischen PPA und FFA angeguckt, aber diesen Unterschied im
Kontrast zu object-related Sentences (dortige Fig 3; lass uns kurz im Gespräch
drübergucken, ich habe die relvanten Abschnitte in der PDF markiert)}

To our knowledge only one study by \citep{aziz2008modulation} correlated
hemodynamic activity of the PPA with spoken sentences.  Sentences described
generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting
pool''), faces  (e.g. ``Marylin Monroe has a large square jaw''), or objects
(e.g. ``The television has a long antenna')'. Participants were instructed to
press a button whenever the sentence described an inaccurate or improbable fact.
Surprisingly, activation in the left, but not right, PPA was significantly
reduced when participants listened to place-related sentences compared to
listening to face-related sentences. Moreover, this effect was only observed in
sentences involving famous places.

@@

% Summary if literature review
In summary, studies suggest that the PPA does not exclusively respond to
visual(ly) spatial information. This is consistent with a competing hypotheses
stating the PPA does not process the spatial layout of a scene specifically but
contextual associations in general (\citep{aminoff2006parahippocampal,
aminoff2013role}). It is still uncertain if auditory stimuli lead to inhibitory
or excitatory responses, or no change at all in the PPA.

@@

% Shortcomings of previous studies; lack of research
All revied studies used a just a small set of carefully designed, simplified
stimuli to strictly control experimental conditions. They further relied on
explicit judgment-based tasks to ensured that participants payed attention to
the stimuli. This raises the question how the PPA behaves under life-like conditions.

\todo[inline]{Data-driven vs. model-driven analyses ist komplett raus; in
Discussion bringen (vgl. Speech-Anno-Paper}

@@

% Literature review naturalistic stimuli: Einleitung
Two early studies using naturalistic stimuli suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [+++ der Schlusssatz ist aus hasson und bartels plagiiert \citep{bartels2004mapping, hasson2004intersubject}+++]

% Bartels (2004): Film + GLM (jedoch ohne PPA) und Hasson (2004)
\citep{bartels2004mapping} manually annotated time points that depict faces and
human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
[+++Ref+++].
Employing a general linear model (GLM) to model hemodynamic activity, these time
points correlated with increased activity in the ``fusiform face area''
\citep{kanwisher1997ffa} and ``extrastriate body area''
\citep{downing2001bodyarea} respectively.

% Hasson (2004): Film + (reverse) ISC
Employing a reverse intersubject correlation, \citep{hasson2004intersubject}
used a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}
[+++Ref+++]. fMRI
brain volumes showing the highest hemodynamic activity in the PPA [across (five)
participants] were matched to the temporally corresponding movie frames.
Results revealed that corresponding movie frames depicted indoor and outdoor
scenes including buildings and open fields.

@@

d) Possibly cite https://psyarxiv.com/sdbqv/ and declare that this study is
a concrete realization of that promise}

\todo[inline]{Präteritum oder Präsens? Ist momentan gemischt; find's ok so}

\todo[inline]{Inner join of AV \& AO: N=14}

% What we did: Einleitung
In this study, we analyze data of three publicly available datasets from the
same set of 14 participants as part of the studyforrest data set
(\href{http://www.studyforrest.org}{studyforrest.org}). We exploratorily
investigate how the parahippocampal gyrus [or more general ``human brain''?]
responds to ``spatially relevant'' events embedded in a 2h audio-visual movie
\citep{hanke2016simultaneous} and its audio-description (i.e. the audio-only
variant) of the same length \citep{hanke2014audiomovie}. We compare these
results to PPA localizations that were obtained from a dedicated visual
localizer experiment \citep{sengupta2016extension}.

Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
We annotated events in the otherwise unknown temporal structure of both stimuli.
In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
Our rationale was that cuts re-orient the viewer in the depicted environment
indepenten from the exact visual content in the movie frame following the cut.
In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.

In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
\todo[inline]{in order to\dots}

Encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like stimulus free from any task to localize a ``visual area'' in individual study participants.

@@

\todo[inline]{Specific data outputs should be explicitly referenced via data
citation (see Data Records and Data Citations, below)}

\todo[inline]{Nach wie vor sind Teile aus den Originalstudien ausführlich}

\todo[inline]{Reihenfolge der subsections mag ``inkorrekt'' sein.}

% intro
We used data from three publicly available datsets, all being part of the
studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org})
which has already been used by other research groups for independent research
questions.
% used studies
The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration}.
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}, a dataset already used by
\citep{ben2018hippocampal}.
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study) \citep{sengupta2016extension}, a dataset aready used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications \citep{hanke2014audiomovie, hanke2016simultaneous,
sengupta2016extension}. Following is a brief summary of most important aspects.

@@

@@

\section*{General Discussion}
% Data-driven vs. Analysis-Driven
% "Abfall" einer Film-Messung
% how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:
% feasibility of (multi-dimensional) localizer development with naturalistic stimuli
% Story für parietale Aktivierung im Film -> räuml. Orientierung / Aufmerksamkeit
% CONFOUNDS als klassisches Gegenargument gg. Filme (aber er ändert sich nicht über die Zeit, vgl. resting state)
% was sind für Film und Audiobook die Confounds?
% Occipital Place Area (Nakamura, 2000), RSC
% Natural stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive, task-free paradigm that more closely resembles our natural dynamic environment than traditional experimental designs. Compared to specifically designed paradigms, the complexity of a natural stimulus goes hand in hand with an unknown temporal structure unless the stimulus is - often manually - annotated \citep{haeusler2016annotation, labs2015portrayed}.
% Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions. This suggests the data can later be reused for variety of totally different, independent research questions, possibly on an individual level.
% aminoffr2013; jedoch zu non-spatial stuff: Although the PHC is commonly thought of as responding to visual stimuli, it has also been found to elicit activity for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].

>>>>

\todo[inline]{our system cannot accept BibTeX bibliography files; authors who
    wish to use BibTeX to prepare their references should therefore copy the
    reference list from the .bbl file that BibTeX generates and paste it into
    the main manuscript .tex file (and delete the associated
    \textbackslash{}bipliography and \textbackslash{}bibliographystyle
commands)}

\section{Introduction} Cognitive neuroscientists use brain imaging methods like
blood oxygenation level-dependent functional magnetic resonance imaging (BOLD
fMRI) to map perceptual and cognitive brain processes (e.g. viewing of
landscapes, \citep{epstein1998ppa}; or theory of mind
\citep{spunt2014validating}) to functional brain areas or networks. Brain
mapping studies have traditionally employed small sets of carefully chosen,
simplified stimuli to strictly control experimental conditions and facilitate
functional isolation of brain areas. The disadvantage is that a limited number
of simplified stimuli does not resemble our real-life experience and lacks
external validity \citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}. Additionally, brain mapping studies usually
average results across at least 10-15 subjects to improve the
signal-to-noise-ratio (SNR). The disadvantage here is that the averaging
approach does not characterize brain functions at an individual level, a
prerequisite for the application of brain imaging methods in individual
diagnostics (cf. \citep{dubois2016building, eickhoff2020towards})

@@

% What is the PPA?
A classic example of a functional, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}. The PPA is located in the posterior parahippocampal
gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus,
both being part of the ventral visual stream \citep{mishkin1982contribution,
goodale1992separate}. Increased hemodynamic activity in the PPA correlates with
the perception of static pictures of landscapes or landmarks compared to
pictures of tools or faces.  According to the spatial layout hypothesis, the PPA
is involved in processing the surface geometry of a visual stimulus and possibly
in identifying scenes based on their spatial layout \citep{epstein2010reliable}.

% Literature Review PPA: Intro
At a group average level, results generalize to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}. One study that used spoken, place-related
sentences showed significantly decreased activation in the left and no
modulation in the right-hemispheric PPA \citep{aziz2008modulation}.

% Exemplary studies
% O'Craven: Mental imagery
In the study conducted by \citep{ocraven2000mental} participants viewed
alternating blocks of pictures showing famous faces and familiar places during
an initial experimental paradigm. In a subsequent paradigm, participants were
instructed to ``form a vivid mental image'' of the previously viewed pictures.
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.

@@

\todo[inline]{Ihre Method Section ist strange und es kommt bei ihr überall eh
    nur uneinheitliche Grütze heraus; Ich blicke nicht durch; was folgend kommt,
    wird nicht vollständig korrekt sein. So wie ich es verstanden habe, hat sie
    den Unterschied zwischen PPA und FFA angeguckt, aber diesen Unterschied im
Kontrast zu object-related Sentences (dortige Fig 3; lass uns kurz im Gespräch
drübergucken, ich habe die relvanten Abschnitte in der PDF markiert)}

To our knowledge only one study by \citep{aziz2008modulation} correlated
hemodynamic activity of the PPA with spoken sentences. Sentences described
generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting
pool''), faces  (e.g. ``Marilyn Monroe has a large square jaw''), or objects
(e.g. ``The television has a long antenna')'. Participants were instructed to
press a button whenever the sentence described an inaccurate or improbable fact.
Surprisingly, activation in the left, but not right, PPA was significantly
reduced when participants listened to place-related sentences compared to
listening to face-related sentences. Moreover, this effect was only observed in
sentences involving famous places.

@@

% Summary if literature review
In summary, studies suggest that the PPA does not exclusively respond to
visual(ly) spatial information. This is consistent with a competing hypotheses
stating that the PPA does not process the spatial layout of a scene specifically
but contextual associations in general (\citep{aminoff2006parahippocampal,
aminoff2013role}). It is still uncertain if auditory stimuli lead to inhibitory
or excitatory responses, or no change at all in the PPA.

@@

% Shortcomings of previous studies; lack of research
All reviewed studies used a just a small set of carefully designed, simplified
stimuli to strictly control experimental conditions. They further relied on
explicit judgment-based tasks to ensure that participants payed attention to
the stimuli. This raises the question how the PPA behaves under life-like conditions.

@@

% Literature review naturalistic stimuli: Einleitung
Two early studies using naturalistic stimuli suggest functional specialization
of brain areas is preserved during movie watching when many perceptual and
cognitive processes are triggered simultaneously \citep{bartels2004mapping, hasson2004intersubject}.

% Bartels (2004): Film + GLM (jedoch ohne PPA) und Hasson (2004)
\citep{bartels2004mapping} manually annotated time points that depict faces and
human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
\citep{tomorrowneverdies}.
Employing a general linear model (GLM) to model hemodynamic activity, these time
points correlated with increased activity in the ``fusiform face area''
\citep{kanwisher1997ffa} and ``extrastriate body area''
\citep{downing2001bodyarea} respectively.

% Hasson (2004): Film + (reverse) ISC
Employing a reverse intersubject correlation, \citep{hasson2004intersubject}
used a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
\citep{goodbadugly} fMRI brain volumes showing the highest hemodynamic activity
in the PPA [across (five) participants] were matched to the temporally
corresponding movie frames. Results revealed that corresponding movie frames
depicted indoor and outdoor scenes including buildings and open fields.

@@

d) Possibly cite https://psyarxiv.com/sdbqv/ (DuPre (2019). Nature abhors a
paywall) and declare that this study is a concrete realization of that promise}

% what we did data source
In this study, we analyze data of three publicly available datasets from the
same set of 14 participants as part of the studyforrest data set
(\href{http://www.studyforrest.org}{studyforrest.org};
\citep{hanke2014audiomovie, hanke2016simultaneous}).
% PPA + movie + audio-description
We annotated cuts in the movie ``Forrest Gump'', and words spoken by an
additional narrator in the movie's audio-description (i.e. the movie's
audio-only variant) to exploratorily investigate how the parahippocampal gyrus
behaves during lifelike stimulation.
% model-driven analysis
In conformity to the analyses performed in the reviewed studies,  we also
employed a standard multi-level, voxel-wise general linear model
(GLM).\todo{why? in order to\dots}
% focus on audio-description
Encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus
on the audio-description as a naturalistic, auditory-only paradigm free from any task to localize a ``visual area'' in individual study participants.
% comparison to dedicated localizer
Finally, we compare our results to results of a dedicated visual localizer
experiment done with the same 14 participants \citep{sengupta2016extension}.

@@

\todo[inline]{Specific data outputs should be explicitly referenced via data
citation (see Data Records and Data Citations, below)}
\todo[inline]{order of subsections possibly wrong}
\todo[inline]{parts from original studies still detailed}

% intro
We used data from three publicly available datasets, all being part of the
studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org})
which has already been used by other research groups for independent research
questions.
% used studies
\todo{this is just loveless listing so far but it's 'complete'}
The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration}.
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}, a dataset already used by
\citep{ben2018hippocampal}.
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study) \citep{sengupta2016extension}, a dataset already used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications \citep{hanke2014audiomovie, hanke2016simultaneous,
sengupta2016extension}. Following is a brief summary of most important aspects.

@@

Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
We annotated events in the otherwise unknown temporal structure of both stimuli.
In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
Our rationale was that cuts re-orient the viewer in the depicted environment
independent from the exact visual content in the movie frame following the cut.
In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.

@@

\section*{General Discussion}
% Data-driven vs. Analysis-Driven
% "Abfall" einer Film-Messung
% how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:
% feasibility of (multi-dimensional) localizer development with naturalistic stimuli
% Story für parietale Aktivierung im Film -> räuml. Orientierung / Aufmerksamkeit
% CONFOUNDS als klassisches Gegenargument gg. Filme (aber er ändert sich nicht über die Zeit, vgl. resting state)
% was sind für Film und Audiobook die Confounds?
% Occipital Place Area (Nakamura, 2000), RSC
% Natural stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive, task-free paradigm that more closely resembles our natural dynamic environment than traditional experimental designs. Compared to specifically designed paradigms, the complexity of a natural stimulus goes hand in hand with an unknown temporal structure unless the stimulus is - often manually - annotated \citep{haeusler2016annotation, labs2015portrayed}.
\todo[inline]{why naturalistic stimuli are so cool: sinkusare2019,
    eickhoff2020}
\todo[inline]{model-driven vs. data-driven analyses}
% Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions. This suggests the data can later be reused for variety of totally different, independent research questions, possibly on an individual level.
% aminoffr2013; jedoch zu non-spatial stuff: Although the PHC is commonly thought of as responding to visual stimuli, it has also been found to elicit activity for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].
